---
title: "Lecture 3"
author: "Tiffany"
date: 2026-09-15
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
---

I'm an R Markdown document! 

# Section 0: Library

```{r load_libraries, message = F}
library(tidyverse)
```


# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3: Tibble

I can create a new data frame.

```{r}
plot_df = 
  tibble(
    x = rnorm(1000, sd = 0.5),
    y = 1 + 2 * x + rnorm(1000),
  )
head(plot_df)
```

# Section 4: Plots

These are plots from our random sample.

```{r echo = F, message = F}
ggplot(plot_df, aes(x = x)) + geom_histogram()

ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

# Section 5: Learning Assessment 2

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

```{r}
la2_df = 
  tibble(
    norm_samp = rnorm(500, mean = 1),
    log_norm_samp = norm_samp > 0,
    abs_norm_samp = abs(norm_samp)
  )
```

```{r}
ggplot(la2_df, aes(x = abs_norm_samp)) + geom_histogram()
```

The median is `r round(median(pull(la2_df, norm_samp)), 2)`.

# Section 6: Formatting

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

# Section 7: Learning Assessment 3

After the previous code chunk, write a bullet list given the mean, median, and standard deviation of the original random sample.

* The mean is `r round(mean(pull(la2_df, norm_samp)), 2)`.

* The median is `r round(median(pull(la2_df, norm_samp)), 2)`.

* The standard deviation is `r round(sd(pull(la2_df, norm_samp)), 2)`.

